*Supplementary Material 2*

### 2022-02-21 ms/si.Rmd
Update SI2 (fossils)
with latest data from ferncal

https://github.com/spiritu-santi/FernsCals/commit/651321d043d58a3a347925a48db590a5b18d6258

```{r fossils-make}
# Filter raw fossil data to just fossils used, write out as CSV
fossils_table <-
  fossil_ferns_raw %>%
  inner_join(
    select(fossil_calibration_tips, fossil_taxon), by = "fossil_taxon") %>%
  verify(nrow(.) == nrow(fossil_calibration_tips)) %>%
  rowwise() %>%
  mutate(
    note = jntools::paste3(notes_21, notes_22sep = ". ") %>%
      str_replace_all("\\.\\.", "\\.") %>%
      na_if(".") %>%
      str_replace_all(" \\.$", "\\.")
  ) %>%
  ungroup() %>%
  select(
    n_fos, minimum_age, node_calibrated, fossil_taxon, 
    lower = lower_limit_of_oldest_stratigraphic_age,
    upper = upper_limit_of_oldest_stratigraphic_age,
    stratigraphic_age, 
    country, type_locality, formation,
    organs, specimen_holotype, collection,
    reference, note
  )
```

>>>>

```{r fossils-make}
# Filter raw fossil data to just fossils used, write out as CSV
fossils_table <-
  fossil_ferns_raw %>%
  inner_join(
    select(fossil_calibration_tips, fossil_taxon), by = "fossil_taxon") %>%
  verify(nrow(.) == nrow(fossil_calibration_tips)) %>%
  select(
    n_fos, minimum_age, node_calibrated, fossil_taxon, 
    lower = lower_limit_of_oldest_stratigraphic_age,
    upper = upper_limit_of_oldest_stratigraphic_age,
    stratigraphic_age, 
    country, type_locality, formation,
    organs, specimen_holotype, collection,
    reference
  )
```

### 2022-02-21 ms/si2.Rmd
Update SI2 (fossils)
with latest data from ferncal

https://github.com/spiritu-santi/FernsCals/commit/651321d043d58a3a347925a48db590a5b18d6258

---
title: "*Supplementary Material 2*"
subtitle: "Fossil Calibration List"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Supplementary Material} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
---

@@

```{r custom-funcs}
#' Print a single category of fossil data
#'
#' @param fossil_data Fossil data in long form, filtered to a single
#' fossil
#' @param cat_select Category of data to print
#'
#' @return Character vector

print_fossil_cat <- function(fossil_data, cat_select) {
  data <-
    fossil_data %>% filter(category == cat_select)

  c(
    md_heading(cat_select, 3),
    md_bullet(data$text),
    md_blank()
  )
}

#' Print data for a single fossil
#'
#' @param fossil_data Fossil data in long form
#' @param fossil_select Selected fossil to print
#'
#' @return Character vector
#'
#' @examples
#' print_fossil(fossils_long, "Acrostichum_intertrappeum") %>%
#' 	glue::as_glue()
print_fossil <- function(fossil_data, fossil_select) {
  # Filter data to only selected fossil
  data <-
    fossils_long %>% filter(fossil_taxon == fossil_select)

  # Print name of fossil as header in italics
  header <-
    data %>% 
    filter(var == "fossil_taxon_header") %>%
    pull(value) %>%
    str_replace_all("_", " ") %>%
    md_italic() %>%
    md_heading(1)

  categories <- data %>%
    filter(!is.na(category)) %>%
    pull(category) %>%
    unique()

  body <- map(categories, ~print_fossil_cat(data, .)) %>%
    unlist()

  c(header, body, md_rule())
}
```

@@

```{r prep-fossil-data}
# Set path to fossil data
fossils_data_path <- here::here("_targets/user/data_raw/Fossils_Ferns.csv")

# Extract fossil categories (first row of fossil data)
fossils_categories <-
  read_csv(fossils_data_path, n_max = 1) %>%
  pivot_longer(names_to = "category", values_to = "raw_names", everything()) %>%
  mutate(
    category = str_replace_all(category, "\\.\\.\\.[0-9]+", "skip") %>%
      na_if("skip")) %>%
  fill(category) %>%
  mutate(category = str_to_title(category)) %>%
  filter(category != "Pteridophy")

# Get raw column names
fossils_raw_names <-
  read_csv(fossils_data_path, skip = 1)

@@

```{r print-fossils, include = TRUE, results = "asis", eval = TRUE}
unique(fossils_long$fossil_taxon) %>%
  map(~print_fossil(fossils_long, .)) %>%
  unlist() %>%
  glue::as_glue()
```

>>>>

---
title: "*Supplementary Material 2*"
subtitle: "Fossil Calibration List"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Supplementary Material} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \setlength{\headheight}{13.6pt}
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
---

@@

```{r load-targets-si-2}
# Targets from MS workflow
tar_load(
  fossil_ferns_path,
  store = here::here("_targets")
)
```

@@

```{r prep-fossil-data}
# Extract fossil categories (first row of fossil data)
fossils_categories <-
  read_csv(fossil_ferns_path, n_max = 1) %>%
  pivot_longer(names_to = "category", values_to = "raw_names", everything()) %>%
  mutate(
    category = str_replace_all(category, "\\.\\.\\.[0-9]+", "skip") %>%
      na_if("skip")) %>%
  fill(category) %>%
  mutate(category = str_to_title(category)) %>%
  filter(category != "Pteridophy")

# Get raw column names
fossils_raw_names <-
  read_csv(fossil_ferns_path, skip = 1)

@@

```{r print-fossils, include = TRUE, results = "asis"}
taxa <- unique(fossils_long$fossil_taxon)

map(taxa, ~print_fossil(fossils_long, .)) %>%
  unlist() %>%
  glue::as_glue()
```
